Title +++
========================================================

OK, so first you load TE package and create a "passport" with your credentials to take full advantage of TE's Database.
Load the library:
```{r}
library(TE)
```
And create the passport using your credentials. You can also take it for a limited ride with guest credentials.
```{r echo=-3:-4}
myUsername = "guest"
myPassword = "guest"
myUsername = "r@tradingeconomics.com"
myPassword = "Lisboa!1"
pp=set.auth(myUsername,myPassword)
```
So now we are ready to start plotting ! For a simple country-indicator plot you can go:
```{r fig.width=9, fig.height=4}
te.plot(pp,"United States","Non Farm Payrolls")
```
You can define the country and indicator variables beforehand to simplify edits. Also, you can add a startDate value to better adjust the chart.
```{r fig.width=9, fig.height=4}
country="United States"
indicator="Unemployment Rate"
startDate="2010-01-01"
te.plot(pp,country,indicator,startDate)
```
To see how Business Condifence and Non Farm Payrrols afect each other:
```{r fig.width=9, fig.height=4}
analyze=c("United States:Business Confidence","United States:Non Farm Payrolls")
te.plot.multi(pp,analyze)
```
And what about more interesting cross-analysis?

Let's say you're interested in vizualizing some data for the G20 Group. Grouping the countries is as easy as:
```{r}
te.countries(pp,"G20")
```
You can also pick any other G-'number'! And what about the fastest 10 growing countries? or the worst 5 performers? 
```{r}
te.countries(pp,"G3")
te.countries(pp,"Emerging10")
te.countries(pp,"Plunging5")
```

Let's select Top 7 American countries and see the how consumer prices have been behaving:
```{r fig.width=9, fig.height=4}
countries=te.countries(pp,"America7")
indicators="Inflation Rate"

te.plot.multi(pp,countries,indicators)
```
And for a latest-value comparison:
```{r fig.width=9, fig.height=4}
te.plot.compare.scale(pp,countries,indicators)
```
All very nice, but how are consumer prices related with GDP Growth in Europe ? 
```{r fig.width=9, fig.height=4}
indicators=c("GDP Annual Growth Rate","Inflation Rate")
countries=te.countries(pp,"Europe10")
te.plot.compare(pp,countries,indicators)
```